Contextuality and the Born rule in fuzzy quantum theories

### 2017-04-10 prop_letter.tex
prop_letter.tex \paragraph{Contextuality Inequality} Updating...

First, notice that his inequality (4)

>>>>

First, although his inequality (4) bases on Mermin square and looks
simple, we cannot use it directly because they are not projectors.
Instead $A_{ij}$ in his equation (1) are almost projectors, because
$A_{ij}=2\proj{v_{ij}}-\mathbb{1}$, and $\ket{v_{ij}}$ are eigenstates
of Mermin square. It is easier to write an inequality start from equation
(1).
